---
title: "flat_bioconsest.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
library(tidyverse)

data(list = c("diet", "species_abundance", "sst", "weight", "map_coords", "beta"))

```


```{r development-load}
pkgload::load_all()
```


# Estimate energyscape and biomass consumption

To estimate the energyscape and prey biomass consumption, we first estimate the energyscape (spatialised energetic need of the population) of a marine predator species (either cetacean, seabirds, loggerhead turtles, sunfish, sharks, tunas or swordfish) from its abundance map and body mass distribution, as well as the sea surface temperature (for fish only). Second, we estimate the daily ration consumed for a given prey group by a single predator individual and the corresponding biomass consumed by the total population. This is done with `bio_cons_est()`, which runs a single estimation, drawing one sample from each provided distribution (body mass, abundance map, SST).


```{r function-bio_cons_est}

#' Estimating energyscape and biomass consumption
#'
#' The function first estimates the energyscape (spatialised energetic need of the population) of a marine predator species (either cetacean, seabirds, loggerhead turtles, sunfish, sharks, tunas or swordfish) from its abundance map and body mass distribution, as well as the sea surface temperature (for fish only). Second, the function estimate the daily ration consumed for a given prey group by a single predator individual and the corresponding biomass consumed by the total population. Results are provided as maps and vectors. This function runs a single estimation. 
#' Allometric relationships are derived from White et al. (2011) with beta parameters from Spitz et al. (2012) for cetaceans; from Ultsch et al. 2013 for loggerhead turtle; from Killen et al. (2016) for fishes and from Shaffer et al. (2011) for seabirds (contrasting Procellariforms and Charadriforms). 
#' 
#' @param predator_group Character. Predator taxonomic group, used to select the allometric equation used to compute the analysis. Can be "Cetacean", "Fish", "Charadriform", "Procellariform", "Loggerhead turtle"
#' @param predator_name Character. Name to be used in exported dataframes
#' @param prey_taxonomic_level Taxonomic level at which the diet is summarize (either "Family", "Taxonomic_group" or "Functional_group", for example), i.e. the column in which prey_group will be subsetted
#' @param prey_group Which level of the diet to select (one of the levels in the chosen prey_taxonomic_level)
#' @param diet Diet table, including the considered predator only. Must include pW (proportion of each item in the diet, as proportion of wet weight), Energy_content of the prey item (in kJ/g) and the column provided in prey_taxonomic_group
#' @param assimilation_rate Assimilation rate to be used to estimate the daily ration (default to 0.8)
#' @param n_days Number of days over which estimating biomas consumption (default to 1)
#' @param beta Vector of life cost parameter, used only for mammals
#' @param predator_weight Vector of body mass distribution for the predator (in kg)
#' @param abundance_map  Abundance map of the predator (must provide columns named mean and sd)
#' @param temperature_map SST map (only used for fish; must provide columns named mean and sd)
#'
#' @return The function returns a list composed of 6 elements: FMR, the energetic needs of a single individuals (kJ/d); abundance, the abubndance map; Energyscape, the energyscape map for the total predator population, for a single day (FMR*abundance; kJ/d); daily_ration, the estimated daily ration (in kg); prop_body_mass, the daily ration expressed as proportion of predator body mass; conso_map, a map of the prey_group biomass consumed by the predator population over the period provided by n_days.
#' 
#' @importFrom glue glue
#' @importFrom assertthat assert_that '%has_name%'
#' @importFrom dplyr mutate summarize select rename
#' @importFrom tidyselect contains
#' 
#' @export
#'
#' @examples
bio_cons_est <- function(predator_group,
                         predator_name,
                       beta = NULL,
                       prey_taxonomic_level, 
                       prey_group, 
                       diet, 
                       assimilation_rate = 0.8, 
                       n_days = 1,
                       predator_weight, # en kg
                       abundance_map, 
                       temperature_map = NULL){
  # checks ----
  if(isFALSE(predator_group %in% c("Cetacean", "Fish", "Procellariform", "Charadriform", "Loggerhead turtle"))){
    stop(glue::glue("{predator_group} is not a supported group of predator"))
  }
  assert_that(is.vector(predator_weight, mode = "numeric"))
  assert_that(is.data.frame(diet))
  assert_that(diet %has_name% c("pW", "Energy_content", prey_taxonomic_level))
  assert_that(is.data.frame(abundance_map))
  assert_that(abundance_map %has_name% c("mean", "sd"))
  
  if(all(isTRUE(predator_group == "Fish"), 
         is.null(temperature_map))){
    stop("you must provide a temperature_map when predator_group is 'Fish'")
  }
  if(all(isTRUE(predator_group == "Fish"), 
         isFALSE(is.data.frame(temperature_map)))){
    stop("temperature_map must be a dataframe")
  }
  if(all(isTRUE(predator_group == "Fish"),
         isFALSE(nrow(abundance_map) == nrow(temperature_map)))){
    stop("abundance_map and temperature_map must have the same length")
  }
  if(all(isTRUE(predator_group == "Fish"), 
         isFALSE(c("mean", "sd") %in% names(temperature_map)))){
    stop("temperature_map must contain mean and sd columns")
  }
  if(all(isTRUE(predator_group %in% c("Cetacean", "Loggerhead turtle")), 
         is.null(beta))){
    stop(glue::glue("you must provide a beta distribution when predator_group is {predator_group}"))
  }
  if(all(isTRUE(predator_group %in% c("Cetacean", "Loggerhead turtle")), 
         isFALSE(is.vector(beta, mode = "numeric")))){
    stop("beta must be a numeric vector")
  }
  
  #### Sample parameters ----
  predator_weight <- sample(predator_weight, size = 1)
  abundance <- as.vector( t( rnorm(n = nrow(abundance_map), 
                            mean = abundance_map[, "mean"], 
                            sd = abundance_map[, "sd"]) ))
  abundance[which(abundance < 0)] <- 0
  # le rnorm fait un tirage aleatoire sur chaque cellule independamment, donc le resultat n'est pas lisse
  
  #### FMR estimation ----
  if(predator_group == "Cetacean"){
    beta <- sample(beta, size = 1)
    BMR <- 4.08*((predator_weight*1000)^0.69) *0.48 # *0.48 to put it from mLO2/h into kJ/d
    FMR <- beta * BMR
    energyscape <- FMR * abundance
  }
  if(predator_group == "Fish"){
    temperature <- as.vector( t( rnorm(n = nrow(temperature_map), 
                                       mean = temperature_map$mean, 
                                       sd = temperature_map$sd) ))
    FMR <- 0.563 * ((predator_weight*1000)^0.937) * exp(0.025 * temperature) * 0.48*0.752  # *0.752 to put it from mgO2/h into kJ/d
    energyscape <- FMR * abundance
  }
  if(predator_group == "Procellariform"){
    FMR <- 23.326*((predator_weight*1000)^0.562)  # Shaffer et al 2011
    # FMR <- 2.149*((predator_weight*1000)^0.804) *3.9 # Ellis&Gabrielsen 2002 + Garthe et al 1996
    energyscape <- FMR * abundance
  }
  if(predator_group == "Charadriform"){
    FMR <- 10.181*((predator_weight*1000)^0.717)
    energyscape <- FMR * abundance
  }
  if(predator_group == "Loggerhead turtle"){
    beta <- sample(beta, size = 1)
    BMR <- 0.674*((predator_weight*1000)^0.649) * 0.48  # *0.48 to put it from mLO2/h into kJ/d
    FMR <- beta * BMR
    energyscape <- FMR * abundance
  }
  
  #### Diet ----
  diet <- diet |>
    dplyr::rename(Prey_category = tidyselect::contains(prey_taxonomic_level)) |> 
    subset(Prey_category == prey_group)
  
  diet_compo <- diet |>
    dplyr::mutate(quality = (pW/100) * Energy_content) |>
    dplyr::summarize(proportion = sum(pW/100, na.rm = T),
                     quality = sum(quality, na.rm = T)) |> as.data.frame() |>
    dplyr::mutate(Predator_key = predator_name)

  
  #### Biomass consumption ----
  # ration journaliere (en kg)
  daily_ration <- ( ( FMR / (assimilation_rate * diet_compo$quality) ) * diet_compo$proportion ) /1000
  
  
  # ration journaliere en proportion du poids corporel
  prop_body_mass <- (daily_ration / predator_weight)*100
  
  # total consumption
  total_biomass <- daily_ration * abundance * n_days
  
  
  #### Return ----
  return(list(
    FMR = FMR,
    abundance = abundance,
    Energyscape = energyscape,
    daily_ration = daily_ration,
    prop_body_mass = prop_body_mass,
    conso_map = total_biomass))
}

```


```{r examples-bio_cons_est}
result <- bio_cons_est(predator_group = "Cetacean",
             predator_name = "TURTRU", 
             prey_taxonomic_level = "Taxonomic_group", 
             prey_group = "Cephalopoda",
             diet = diet, 
             assimilation_rate = 0.8,
             n_days = 30+31+31,
             predator_weight = weight, 
             abundance_map = species_abundance, 
             temperature_map = sst,
             beta = beta) # not used for fishes and seabirds

```


```{r tests-bio_cons_est}
test_that("bio_cons_est() returns a list", {
  expect_true(
    object = inherits(
      bio_cons_est(predator_group = "Cetacean",
               predator_name = "TURTRU", 
               prey_taxonomic_level = "Taxonomic_group", 
               prey_group = "Cephalopoda",
               diet = diet, 
               assimilation_rate = 0.8,
               n_days = 30+31+31,
               predator_weight = weight, 
               abundance_map = species_abundance, 
               temperature_map = sst, # not used for cetaceans and seabirds
               beta = 3),
      "list")
    )
  
  expect_error(
    object = bio_cons_est(predator_group = "Cetacean",
               predator_name = "TURTRU", 
               prey_taxonomic_level = "Taxonomic_group", 
               prey_group = "Cephalopoda",
               diet = diet, 
               assimilation_rate = 0.8,
               n_days = 30+31+31,
               predator_weight = weight, 
               abundance_map = species_abundance, 
               temperature_map = sst, # not used for cetaceans and seabirds
               beta = NULL),
    regexp = "you must provide a beta distribution when predator_group is Cetacean"
  )
  
  expect_error(
    object = bio_cons_est(predator_group = "Fish",
               predator_name = "TURTRU", 
               prey_taxonomic_level = "Taxonomic_group", 
               prey_group = "Cephalopoda",
               diet = diet, 
               assimilation_rate = 0.8,
               n_days = 30+31+31,
               predator_weight = weight, 
               abundance_map = species_abundance, 
               temperature_map = NULL),
    regexp = "you must provide a temperature_map when predator_group is 'Fish'"
  )
}
  
)
```



# Monte Carlo simulation

To obtain the final estimations, we embed this function into a Monte Carlo simulation which runs it how many times is required to obtain a reliable estimate. This number of simulation is set to 1000 by default but can be changed by the user. 


```{r function-mc_simulation}
#' Estimating energyscape and biomass consumption with Monte Carlo simulations
#'
#' Function to run the Monte Carlo simulation for energyscape and biomass estimations. This functions identifies the prey levels as defined by the prey_taxonomic_level, drop any item for which pW or Energy_content is missing, runs the \code{\link{bio_cons_est}} function n_sim times for each item, extracts the posterior distributions of each estimated parameter and returns the summarized results for all levels in prey_taxonomic_level. 
#'  
#' @importFrom glue glue
#' @importFrom dplyr mutate summarize select rename pull
#' @importFrom tidyselect contains any_of
#' @importFrom tidyr drop_na
#' @importFrom purrr map
#' @importFrom assertthat assert_that '%has_name%'
#' 
#' @param nsim The number of simulations to run; 1000 by default
#' @param map_coordinates data.frame containing x and y coordinates of the map
#' @inheritParams bio_cons_est
#' 
#' @return  The function returns a list of 8 elements: FMR_map, the map of FMR (kJ/d); Energyscape_map, the energyscape map (kJ/d; FMR * abundance), with the abundance of the species (columns named N_); DailyRation_map, the map of daily ration (kg); DailyRationPropBM_map, the same but as proportion of body mass; DailyRation, the estimated daily ration averaged over the map (as a table; in kg); DailyRationPropBM, the same as proportion of body mass; Conso_map, the map of total consumed biomass (in kg) and Conso, the consumed biomass summed over the map (in kg). When more than one category exists for a prey_taxonomic_level, maps are returned as tables in a long format (directly usable with facetting in ggplot), except for FMR and Energyscape which return the maps estimated with the first category (for these two elements, the result is the same with any prey_group).
#' 
#' 
#' @export
#'
#' @examples
mc_simulation <- function(predator_name, 
                          predator_group, 
                       map_coordinates,
                       beta = NULL,
                       prey_taxonomic_level, 
                       diet, 
                       assimilation_rate = 0.8, 
                       n_days = 1,
                       predator_weight, # en kg
                       abundance_map, 
                       temperature_map = NULL,
                       nsim = 1000){
  # check map_coords
  assert_that(map_coordinates %has_name% c("x", "y"))

  # extract the prey category in the requested taxonomic level ----
  diet <- diet |> tidyr::drop_na(tidyselect::any_of(c("pW", "Energy_content", prey_taxonomic_level)))
  levels <- unique(dplyr::pull(diet, prey_taxonomic_level))
  if(length(levels) == 0) {
    stop(glue::glue("No prey categories in {prey_taxonomic_level} for {predator_name}"))
  }
  if(length(levels) == 1) {
    # Run the simulation
    MC_sim <- pbapply::pblapply(1:nsim, function(i){
      toto <- bio_cons_est(predator_name = predator_name, 
                           predator_group = predator_group,
                 prey_taxonomic_level = prey_taxonomic_level, 
                 prey_group = levels,
                 diet = diet, 
                 assimilation_rate = assimilation_rate,
                 n_days = n_days,
                 predator_weight = predator_weight, 
                 abundance_map = abundance_map, 
                 temperature_map = temperature_map,
                 beta = beta)
    })
  
    # Extract and format the results
    ## FMR
    posterior_FMR <- MC_sim |> 
      purrr::map(`[[`, "FMR") |> # ou purrr::map(`[[`, 1)
      do.call(what = "cbind") # a map array for fish, a vector for others
    
    smry_FMR_map <- data.frame(
      x = map_coordinates$x,
      y = map_coordinates$y,
      FMR_mean = apply( posterior_FMR, 1, "mean"),
      FMR_sd = apply( posterior_FMR, 1, "sd"),
      FMR_L10 = apply( posterior_FMR, 1, function(i){quantile(i, probs = 0.10)}),
      FMR_U90 = apply( posterior_FMR, 1, function(i){quantile(i, probs = 0.90)}),
      Prey_category = levels,
      Predator_key = predator_name
    )
    
    ## Abundance and energyscapes
    posterior_ab <- MC_sim |> 
      purrr::map(`[[`, "abundance") |> # ou purrr::map(`[[`, 1)
      do.call(what = "cbind") # a map array for fish, a vector for others
    
    posterior_Energyscape <- MC_sim |> 
      purrr::map(`[[`, "Energyscape") |>
      do.call(what = "cbind") # an map array
    
    smry_Energyscape <- data.frame(
      x = map_coordinates$x,
      y = map_coordinates$y,
      N_mean = apply( posterior_ab, 1, "mean"),
      N_sd = apply( posterior_ab, 1, "sd"),
      N_L10 = apply( posterior_ab, 1, function(i){quantile(i, probs = 0.10)}),
      N_U90 = apply( posterior_ab, 1, function(i){quantile(i, probs = 0.90)}),
      Energyscape_mean = apply( posterior_Energyscape, 1, "mean"),
      Energyscape_sd = apply( posterior_Energyscape, 1, "sd"),
      Energyscape_L10 = apply( posterior_Energyscape, 1, function(i){quantile(i, probs = 0.10)}),
      Energyscape_U90 = apply( posterior_Energyscape, 1, function(i){quantile(i, probs = 0.90)}),
      Prey_category = levels,
      Predator_key = predator_name
    )
    
    ## Daily ration
    posterior_Ration <- MC_sim |> 
      purrr::map(`[[`, "daily_ration") |>
      do.call(what = "cbind") # a map array for fish, a vector for the others
    
    smry_Ration_map <- data.frame(
      x = map_coordinates$x,
      y = map_coordinates$y,
      Ration_mean = apply( posterior_Ration, 1, "mean"),
      Ration_sd = apply( posterior_Ration, 1, "sd"),
      Ration_L10 = apply( posterior_Ration, 1, function(i){quantile(i, probs = 0.10)}),
      Ration_U90 = apply( posterior_Ration, 1, function(i){quantile(i, probs = 0.90)}),
      Prey_category = levels,
      Predator_key = predator_name
    )
    
    smry_Ration <- data.frame(
      mean = mean(smry_Ration_map$Ration_mean),
      sd = mean(smry_Ration_map$Ration_sd),
      L10 = quantile(smry_Ration_map$Ration_L10, probs = 0.10),
      U90 = quantile(smry_Ration_map$Ration_U90, probs = 0.90),
      Prey_category = levels,
      Predator_key = predator_name
    )
    
    ## Daily ration prop body mass
    posterior_RationPropBM <- MC_sim |> 
      purrr::map(`[[`, "prop_body_mass") |>
      do.call(what = "cbind")
    
    smry_RationPropBM_map <- data.frame(
      x = map_coordinates$x,
      y = map_coordinates$y,
      RationPropBM_mean = apply( posterior_RationPropBM, 1, "mean"),
      RationPropBM_sd = apply( posterior_RationPropBM, 1, "sd"),
      RationPropBM_L10 = apply( posterior_RationPropBM, 1, function(i){quantile(i, probs = 0.10)}),
      RationPropBM_U90 = apply( posterior_RationPropBM, 1, function(i){quantile(i, probs = 0.90)}),
      Prey_category = levels,
      Predator_key = predator_name
    )
    
    smry_RationPropBM <- data.frame(
      mean = mean(smry_RationPropBM_map$RationPropBM_mean),
      sd = mean(smry_RationPropBM_map$RationPropBM_sd),
      L10 = quantile(smry_RationPropBM_map$RationPropBM_L10, probs = 0.10),
      U90 = quantile(smry_RationPropBM_map$RationPropBM_U90, probs = 0.90),
      Prey_category = levels,
      Predator_key = predator_name
    )
    
    # ConsoMap
    posterior_ConsoMap <- MC_sim |> 
      purrr::map(`[[`, "conso_map") |>
      do.call(what = "cbind")
    
    smry_ConsoMap_map <- data.frame(
      x = map_coordinates$x,
      y = map_coordinates$y,
      ConsoMap_mean = apply( posterior_ConsoMap, 1, "mean"),
      ConsoMap_sd = apply( posterior_ConsoMap, 1, "sd"),
      ConsoMap_L10 = apply( posterior_ConsoMap, 1, function(i){quantile(i, probs = 0.10)}),
      ConsoMap_U90 = apply( posterior_ConsoMap, 1, function(i){quantile(i, probs = 0.90)}),
      Prey_category = levels,
      Predator_key = predator_name
    )
    
    smry_ConsoMap <- data.frame(
      mean = sum(smry_ConsoMap_map$ConsoMap_mean),
      sd = sum(smry_ConsoMap_map$ConsoMap_sd),
      L10 = sum(smry_ConsoMap_map$ConsoMap_L10),
      U90 = sum(smry_ConsoMap_map$ConsoMap_U90),
      Prey_category = levels,
      Predator_key = predator_name
    )
    
    # return the result tables
    return(list(
      FMR_map = smry_FMR_map, 
      Energyscape = smry_Energyscape, 
      DailyRation_map = smry_Ration_map, 
      DailyRation = smry_Ration, 
      DailyRationPropBM_map = smry_RationPropBM_map, 
      DailyRationPropBM = smry_RationPropBM, 
      Conso_map = smry_ConsoMap_map, 
      Conso = smry_ConsoMap
    ))
  }
  if(length(levels) > 1){
    # compute mc_sim for each level separately
    prey_loop <- lapply(1:length(levels), function(i){
      message(paste0("Computing ", levels[i], " for ", predator_name))
      # Run the simulation
      MC_sim <- pbapply::pblapply(1:nsim, function(j){
        toto <- bio_cons_est(predator_name = predator_name, 
                           predator_group = predator_group,
                 prey_taxonomic_level = prey_taxonomic_level, 
                 prey_group = levels[i],
                 diet = diet, 
                 assimilation_rate = assimilation_rate,
                 n_days = n_days,
                 predator_weight = predator_weight, 
                 abundance_map = abundance_map, 
                 temperature_map = temperature_map,
                 beta = beta)
      })
    
      # Extract and format the results ----
      ## FMR
      posterior_FMR <- MC_sim |> 
        purrr::map(`[[`, "FMR") |>
        do.call(what = "cbind") # a map array for fish, a vector for others
      
      smry_FMR_map <- data.frame(
        x = map_coordinates$x,
        y = map_coordinates$y,
        FMR_mean = apply( posterior_FMR, 1, "mean"),
        FMR_sd = apply( posterior_FMR, 1, "sd"),
        FMR_L10 = apply( posterior_FMR, 1, function(i){quantile(i, probs = 0.10)}),
        FMR_U90 = apply( posterior_FMR, 1, function(i){quantile(i, probs = 0.90)})
      )
      
      ## Abundance and energyscapes
      posterior_ab <- MC_sim |> 
        purrr::map(`[[`, "abundance") |> # ou purrr::map(`[[`, 1)
        do.call(what = "cbind") # a map array for fish, a vector for others
      
      posterior_Energyscape <- MC_sim |> 
        purrr::map(`[[`, "Energyscape") |>
        do.call(what = "cbind") # an map array
      
      smry_Energyscape <- data.frame(
        x = map_coordinates$x,
        y = map_coordinates$y,
        N_mean = apply( posterior_ab, 1, "mean"),
        N_sd = apply( posterior_ab, 1, "sd"),
        N_L10 = apply( posterior_ab, 1, function(i){quantile(i, probs = 0.10)}),
        N_U90 = apply( posterior_ab, 1, function(i){quantile(i, probs = 0.90)}),
        Energyscape_mean = apply( posterior_Energyscape, 1, "mean"),
        Energyscape_sd = apply( posterior_Energyscape, 1, "sd"),
        Energyscape_L10 = apply( posterior_Energyscape, 1, function(i){quantile(i, probs = 0.10)}),
        Energyscape_U90 = apply( posterior_Energyscape, 1, function(i){quantile(i, probs = 0.90)}),
        Prey_category = levels[i],
        Predator_key = predator_name
      )
      
      ## Daily ration
      posterior_Ration <- MC_sim |> 
        purrr::map(`[[`, "daily_ration") |>
        do.call(what = "cbind") # a map array for fish, a vector for the others
      
      smry_Ration_map <- data.frame(
        x = map_coordinates$x,
        y = map_coordinates$y,
        Ration_mean = apply( posterior_Ration, 1, "mean"),
        Ration_sd = apply( posterior_Ration, 1, "sd"),
        Ration_L10 = apply( posterior_Ration, 1, function(i){quantile(i, probs = 0.10)}),
        Ration_U90 = apply( posterior_Ration, 1, function(i){quantile(i, probs = 0.90)}),
        Prey_category = levels[i],
        Predator_key = predator_name
      )
      
      smry_Ration <- data.frame(
        mean = mean(smry_Ration_map$Ration_mean),
        sd = mean(smry_Ration_map$Ration_sd),
        L10 = quantile(smry_Ration_map$Ration_L10, probs = 0.10),
        U90 = quantile(smry_Ration_map$Ration_U90, probs = 0.90),
        Prey_category = levels[i],
        Predator_key = predator_name
      )
      
      ## Daily ration prop body mass
      posterior_RationPropBM <- MC_sim |> 
        purrr::map(`[[`, "prop_body_mass") |>
        do.call(what = "cbind")
      
      smry_RationPropBM_map <- data.frame(
        x = map_coordinates$x,
        y = map_coordinates$y,
        RationPropBM_mean = apply( posterior_RationPropBM, 1, "mean"),
        RationPropBM_sd = apply( posterior_RationPropBM, 1, "sd"),
        RationPropBM_L10 = apply( posterior_RationPropBM, 1, function(i){quantile(i, probs = 0.10)}),
        RationPropBM_U90 = apply( posterior_RationPropBM, 1, function(i){quantile(i, probs = 0.90)}),
        Prey_category = levels[i],
        Predator_key = predator_name
      )
      
      smry_RationPropBM <- data.frame(
        mean = mean(smry_RationPropBM_map$RationPropBM_mean),
        sd = mean(smry_RationPropBM_map$RationPropBM_sd),
        L10 = quantile(smry_RationPropBM_map$RationPropBM_L10, probs = 0.10),
        U90 = quantile(smry_RationPropBM_map$RationPropBM_U90, probs = 0.90),
        Prey_category = levels[i],
        Predator_key = predator_name
      )
      
      # ConsoMap
      posterior_ConsoMap <- MC_sim |> 
        purrr::map(`[[`, "conso_map") |>
        do.call(what = "cbind")
      
      smry_ConsoMap_map <- data.frame(
        x = map_coordinates$x,
        y = map_coordinates$y,
        ConsoMap_mean = apply( posterior_ConsoMap, 1, "mean"),
        ConsoMap_sd = apply( posterior_ConsoMap, 1, "sd"),
        ConsoMap_L10 = apply( posterior_ConsoMap, 1, function(i){quantile(i, probs = 0.10)}),
        ConsoMap_U90 = apply( posterior_ConsoMap, 1, function(i){quantile(i, probs = 0.90)}),
        Prey_category = levels[i],
        Predator_key = predator_name
      )
      
      smry_ConsoMap <- data.frame(
        mean = sum(smry_ConsoMap_map$ConsoMap_mean),
        sd = sum(smry_ConsoMap_map$ConsoMap_sd),
        L10 = sum(smry_ConsoMap_map$ConsoMap_L10),
        U90 = sum(smry_ConsoMap_map$ConsoMap_U90),
        Prey_category = levels[i],
        Predator_key = predator_name
      )
      
      # return the result tables
      return(list(
        FMR_map = smry_FMR_map, 
        Energyscape_map = smry_Energyscape, 
        DailyRation_map = smry_Ration_map, 
        DailyRation = smry_Ration, 
        DailyRationPropBM_map = smry_RationPropBM_map, 
        DailyRationPropBM = smry_RationPropBM, 
        Conso_map = smry_ConsoMap_map, 
        Conso = smry_ConsoMap
      ))
    })
    
    message("Wrapping up")
    # wrapping tables
    smry_DailyRation <- prey_loop |> 
        purrr::map(`[[`, "DailyRation") |>
        do.call(what = "rbind") 
    smry_DailyRationPropBM <- prey_loop |> 
        purrr::map(`[[`, "DailyRationPropBM") |>
        do.call(what = "rbind") 
    smry_Conso <- prey_loop |> 
        purrr::map(`[[`, "Conso") |>
        do.call(what = "rbind") 
    
    # wrapping maps
    smry_FMR_map <- prey_loop[[1]]$FMR_map
    smry_Energyscape <- prey_loop[[1]]$Energyscape_map 
    smry_DailyRation_map <- prey_loop |> 
        purrr::map(`[[`, "DailyRation_map") |>
        do.call(what = "rbind") 
    smry_DailyRationPropBM_map <- prey_loop |> 
        purrr::map(`[[`, "DailyRationPropBM_map") |>
        do.call(what = "rbind") 
    smry_Conso_map <- prey_loop |> 
        purrr::map(`[[`, "Conso_map") |>
        do.call(what = "rbind") 
    
    return(list(
      FMR_map = smry_FMR_map, 
      Energyscape = smry_Energyscape, 
      DailyRation = smry_DailyRation, 
      DailyRationPropBM = smry_DailyRationPropBM, 
      Conso = smry_Conso,
      DailyRation_map = smry_DailyRation_map, 
      DailyRationPropBM_map = smry_DailyRationPropBM_map, 
      Conso_map = smry_Conso_map))
  }
}
```


```{r examples-mc_simulation}
# test mc_simulation() with one prey level
TURTRU_result <- mc_simulation(predator_name = "TURTRU", 
                               predator_group = "Cetacean",
             map_coordinates = map_coords,
             prey_taxonomic_level = "Taxonomic_group", 
             diet = diet |> subset(Taxonomic_group == "Cephalopoda"), 
             assimilation_rate = 0.8,
             n_days = 30+31+31,
             predator_weight = weight, 
             abundance_map = species_abundance, 
             temperature_map = sst, # not used for cetaceans and seabirds
             beta = beta)

# test mc_simulation() with 2 prey levels
TURTRU_result <- mc_simulation(predator_name = "TURTRU", 
                               predator_group = "Cetacean",
             map_coordinates = map_coords,
             prey_taxonomic_level = "Taxonomic_group", 
             diet = diet, 
             assimilation_rate = 0.8,
             n_days = 30+31+31,
             predator_weight = weight, 
             abundance_map = species_abundance, 
             temperature_map = sst, # not used for cetaceans and seabirds
             beta = beta)

# plot results
ggplot2::ggplot(TURTRU_result$Conso) +
    ggplot2::geom_pointrange(ggplot2::aes(y = Prey_category, x = mean, xmin = L10, xmax = U90))

ggplot2::ggplot(TURTRU_result$Energyscape) +
  ggplot2::geom_tile(ggplot2::aes(x = x, y = y, fill = Energyscape_mean))


```


```{r tests-mc_simulation}
test_that("mc_simulation() returns an error when no prey category in the provided prey_taxonomic_level",
  expect_error(
    object = mc_simulation(predator_name = "TURTRU", 
                           predator_group = "Cetacean",
             map_coordinates = map_coords,
             prey_taxonomic_level = "Taxonomic_group", 
             diet = diet |> subset(Taxonomic_group == "Krill"), 
             assimilation_rate = 0.8,
             n_days = 30+31+31,
             predator_weight = weight, 
             abundance_map = species_abundance, 
             temperature_map = NULL, # not used for cetaceans and seabirds
             beta = beta),
    regexp = "No prey categories in Taxonomic_group for TURTRU"
  )
)
```




```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_bioconsest.Rmd", 
               vignette_name = "Energyscape of top predator",
               overwrite = TRUE, check = F)
```

